Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-14 manuscript.tex
English improvements in aesthetics section (intro + ligeti intro)

In this section I analyze musical concepts as described in \textbf{written materials} of the three composers.
For each composer I analyze one written source:
for Ligeti, I analyze ``Ligeti in conversation'' --- an interview that was conducted by Peter Varnai in 1983 (\cite{varnai});
for Stockhausen, I analyze his 1962 paper ``The concept of unity in electronic music'' (\cite{stockhausen});
and for Koenig, I analyze his 1963 paper ``The Construction of Sound'' (\cite{koenig}).

This work deals with aesthetics of electronic music, hence the decision to choose these papers by Stockhausen and Koenig is trivial.
On the other hand, for Ligeti I choose a source with broader perspective, as he cannot be described as an electronic composer.
Varnai's interview of Ligeti presents a comprehensive set of ideas behind Ligeti's composition style, and I found it useful as a basis to comparisons of musical concepts.

@@

The following is a curated list musical concepts that I have collected from Ligeti's interview.
The description of each concept is quoted directly from the interview.
I add additional clarification only when absolutely necessary, as I think that the concepts are relatively self-explanatory, by Ligeti's words.

>>>>

In this section I analyze musical concepts as described in \textbf{written materials} by the three composers.
For each composer I analyze one written source:
for Ligeti, I analyze ``Ligeti in conversation'' --- an interview that was conducted by Peter Varnai in 1983 (\cite{varnai});
for Stockhausen, I analyze his 1962 paper ``The concept of unity in electronic music'' (\cite{stockhausen});
and for Koenig, I analyze his 1963 paper ``The Construction of Sound'' (\cite{koenig}).

This work deals with aesthetics of electronic music, hence the decision to choose these papers by Stockhausen and Koenig is trivial.
On the other hand, for Ligeti I choose a source with broader perspective, as his music is usually not categorized as electronic.
Varnai's interview of Ligeti presents a comprehensive set of ideas behind Ligeti's composition style, and I found it useful as a basis to compare the musical concepts with.

@@

The following is a curated list musical concepts that I have collected from Ligeti's interview.
The description of each concept is quoted directly from the interview.
I add additional clarification only when absolutely necessary, as I think that the concepts are relatively self-explanatory, in Ligeti's words.
